Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2020)

### 2020-07-14 ICML/example_paper.tex
ICML proposal in correct format, minor changes to thesis manuscript (typo, figure label, etc.)
Recompile ATREMISS submission with correct style file

%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

@@

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
\usepackage{hyperref}

@@

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2020}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2020}

@@

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{37}^{th}$ International Conference on Machine Learning},
Vienna, Austria, 2020.
Copyright 2020 by the author(s).''

>>>>

%%%%%%%% Artemiss 2020 ICML EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

@@

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{artemiss2020icml} with \usepackage[nohyperref]{artemiss2020icml} above.
\usepackage{hyperref}

@@

% Use the following line for the initial blind version submitted for review:
%\usepackage{artemiss2020icml}

% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{artemiss2020icml}

@@

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{37}^{th}$ International Conference on Machine Learning},
Vienna, Austria, PMLR 119, 2020.
Copyright 2020 by the author(s).''
